\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-03-31 docs/paper/paper.tex
Few changes

Machine Learning (ML) techniques are coming to the forefront of many fields, surpassing human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology. Artificial Neural Networks can approximate any function by virtue of the Universality theorem: No matter what the input is there is to be a guaranteed ANN architecture that computes the desired outputs. This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures \cite{kiarashinejad2020knowledge}, optimization of photonic crystal nanocavities \cite{asano2018optimization}, and more recently, computing optical properties of a photonic crystal fiber \cite{chugh2019machine}.

@@

In this paper we focus on determining one of the propagation features of a unique multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), proposed in our recent work [21], that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model, as demonstrated in Figure(1). We will fix the pattern and geometrical shape of the cladding air holes, and vary the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$. Then the results of this study can be carried to different types of SPR-based PCF sensors, using other suitable deep learning approaches such as Recurrent and Convolutional neural networks.

>>>>

Machine Learning (ML) techniques are coming to the forefront of many fields, surpassing human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology. Additionally, ANN can approximate any function proven by Universality theorem \cite{HORNIK1991251}. This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures \cite{kiarashinejad2020knowledge}, optimization of photonic crystal nanocavities \cite{asano2018optimization}, and more recently, computing optical properties of a photonic crystal fiber \cite{chugh2019machine}.

@@

In this paper, we focus on estimating confinement loss, one of the propagation features of multi-channel Photonic Crystal Fiber (PCF) sensors, using artificial neural networks. Specifically, we have based our system on Surface Plasmon Resonance (SPR).

\hl{CK: Continuing from here...}

\hl{and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model, as demonstrated in Figure(1). We will fix the pattern and geometrical shape of the cladding air holes, and vary the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$. Then the results of this study can be carried to different types of SPR-based PCF sensors, using other suitable deep learning approaches such as Recurrent and Convolutional neural networks. }
